---
title: "REGRESSION MODELING OF REAL ESTATE DATA"
author: "INDRESH SINGH ( 215280011)"
date: "15/12/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# REGRESSION MODEL OF REAL ESTAE DATASET



## All About Dataset 
Name of Dataset :- Real Estate data 
Source :- https://www.kaggle.com/dcw8161/real-estate-price-prediction/data
Variables :- 1) X1 transaction date (Date at which home is bought)
             2) X2 house age (age of house from when it was built)
             3) X3 distance to the nearest MRT station
             4) X4 number of convenience stores
             5) X5 latitude ( represents the geographical position of property)
             6) X6 longitude ( represents geographical position of property )
             7) Y house price of unit area
      
Dimensions :- 414 × 8       



```{r}
setwd("C:\\Users\\Indresh Singh\\OneDrive\\Desktop\\Project")
```

### Reading the data as Real_df


```{r}
Real_df=read.csv('Real estate.csv' , header=TRUE)
head(Real_df)
```

```{r}
str(Real_df)
```

```{r}
dim(Real_df)
```

```{r}
summary(Real_df)
```
```{r}
library(tidyverse)
sum(is.na(Real_df))
```
our data doesnt contain any N.A. values hence it is good to define a linear regression model

# model fitting 


```{r}
model1=lm(Y.house.price.of.unit.area~. , Real_df)
summary(model1)
```
considering a level of significance to be 1% 
It is found that No is just a observation number and also found to be insignificant for prediction of house price of unit area
also transaction date can not be treated as predictor variable since it is not a numeric. transaction date defines time factor which we are not considering in our model. hence it should be removed from Model. 
so we define new model after removing ${\bf No.and\ transaction\ date }$

```{r}
model2=lm(Y.house.price.of.unit.area ~ .-No -X1.transaction.date , Real_df)
summary(model2)
```
 again in newly defined model ${\bf X6\ longitude}$  is ${\bf insignificant}$ hence  we will remove it from model. 
 and define our model which will give us better results than before 

```{r}
model3=lm(Y.house.price.of.unit.area ~ .-No -X1.transaction.date-X6.longitude , Real_df)
summary(model3)
```
even though after removing  ${\bf X6\ longitude}$ our R-SQUARED value havent increased significantly but we got the model with all significant predictors  
hence we will do some dignosis of model3 using plots 

### model diagnosis of model 3


```{r}
library(ggplot2)
library(ggfortify)
autoplot(model3)
```


from above plots it is clear that 
1) except some earlier observations line's behovior is little non linear 
2) From normal Q-Q plot we can conclude that normality is satisfied except extreme values 
3) data is homoscedastic 
4) some observations aer to be treated as liverage points 

## check for multicollineary 

```{r}
library(carData)
library(car)
vif(model3)
```
since VIF ( variance inflation factor) is less than 5 for all the predictors involved we can say that ${\bf  Multicolinearity}$ is${\bf  not\ present}$ in the model 3

## checking For Presence of interaction terms 

we will check the prescence of interaction terms using ${\bf  Corrplot}$ 



```{r}
library(corrplot)
corrplot(cor(Real_df),type="upper",method="circle",title="Correlation plot between variables",
         mar=c(0.7,0.7,0.7,0.7),tl.cex = 0.6)
```
From above corrplot we can conclude that there is correlation bewteen following pairs of variables

1)X4.number.of.convenience.stores , X3.distance.to.the.nearest.MRT.station
2)X3.distance.to.the.nearest.MRT.station ,  X5.latitude
3)X3.distance.to.the.nearest.MRT.station ,  X6.longitude
4)X4.number.of.convenience.stores ,  X5.latitude


```{r}
cor(Real_df$X4.number.of.convenience.stores , Real_df$X3.distance.to.the.nearest.MRT.station)
cor(Real_df$X3.distance.to.the.nearest.MRT.station , Real_df$X5.latitude)
cor(Real_df$X3.distance.to.the.nearest.MRT.station , Real_df$X6.longitude)
cor(Real_df$X4.number.of.convenience.stores , Real_df$X5.latitude)

```


1)cor(X4.number.of.convenience.stores , X3.distance.to.the.nearest.MRT.station) is ${\bf -0.6025191}$
2)cor(X3.distance.to.the.nearest.MRT.station ,  X5.latitude) is  ${\bf -0.5910666}$
3)cor(X3.distance.to.the.nearest.MRT.station ,  X6.longitude) is  ${\bf -0.8063168}$
4)cor(X4.number.of.convenience.stores ,  X5.latitude) is   ${\bf 0.4441433}$



correlation between  ${\bf X3.distance.to.the.nearest.MRT.station\ and\ X6.longitude}$ is very high but X6.longitude is not included in model so their interaction term is not added in the forthcoming model 
Interaction terms of following terms are added in  model4
1)X4.number.of.convenience.stores , X3.distance.to.the.nearest.MRT.station
2)X3.distance.to.the.nearest.MRT.station ,  X5.latitude



```{r}
model4=lm(Y.house.price.of.unit.area ~ .-No -X1.transaction.date-X6.longitude + X4.number.of.convenience.stores :X3.distance.to.the.nearest.MRT.station + X3.distance.to.the.nearest.MRT.station : X5.latitude , Real_df )
summary(model4)
```
model4 is model after addition of interaction terms 


```{r}
autoplot(model4)
```
#####  from liverage plot observations 271 , 345 and 229 are found to be livearage points and removing them will yeild some efficiency in the model 
  
  
```{r}
Real_df1=Real_df[-c(271 , 345 , 229),]
dim(Real_df1)
```

##### so clearly liverage points are removed in newly stored datset Real_df1 , so we will redefine model using this dataset Real_df1
  
```{r}
model5=lm(Y.house.price.of.unit.area ~ .-No -X1.transaction.date-X6.longitude + X4.number.of.convenience.stores :X3.distance.to.the.nearest.MRT.station + X3.distance.to.the.nearest.MRT.station : X5.latitude , Real_df1 )
summary(model5)
```
#####  we can clearly see 5% increament in the efficeincy of model5 after removal of liverage points which indicates improvement in model 
   
   
## Adding Polynomial terms in the model   
   since X2.house.age & X3.distance.to.the.nearest.MRT.station have least p values we tested models adding higher powers of these two varible , I defined some test models and expremented with them ( all those test models are not mentioned here) and got following model with appropriate polynomial terms.
we will define that model as Test_odel
   
```{r}
Test_model=lm(Y.house.price.of.unit.area ~ .-No -X1.transaction.date-X6.longitude + X4.number.of.convenience.stores :X3.distance.to.the.nearest.MRT.station + X3.distance.to.the.nearest.MRT.station : X5.latitude+I(X2.house.age^2)+I(X3.distance.to.the.nearest.MRT.station^2), Real_df1 )

summary(Test_model)
```

### analysis from plots of Test model 

```{r}
autoplot(Test_model)
```

since value of ${\bf R-Squared }$ is 71.64 % we conclude that Test_model is our  Final model


## Final model is 

 Y.house.price.of.unit.area =  -1.001e+04 -(1.019e+00)X2.house.age+(2.408e+00)X3.distance.to.the.nearest.MRT.station + ( 1.144e+00)X4.number.of.convenience.stores+(4.030e+02)X5.latitude+(1.857e-02)(X2.house.age^2)+(6.692e-07)(X3.distance.to.the.nearest.MRT.station^2)-(7.870e-04)[X3.distance.to.the.nearest.MRT.station:X4.number.of.convenience.stores]-(9.674e-02)[X3.distance.to.the.nearest.MRT.station:X5.latitude]


## Conclusion of the final model: 

1) R-Squared value of our final model is 71.64% .
2) From the residual vs fitted graph we can see that the estimated error curve of our final model is almost converge to 0.
3) From the QQ-Plot we can see that the our model behaves like normal except for the tail parts.
4) Data is homoscedastic 



